### 2020-03-14 papers.tex
Add "triple" "blind" review for paper 16
Add belated paper 6
Add a slew of new papers that arrived for the Friday the 13th planned deadline

@@

>>>>

	{SIGBOVIK_2020_paper_6}

@@

\addreview{SIGBOVIK_2020_review_8}{0cm}
	{GradSchoolNet:\@ Robust end-to-end *-shot unsupervised deepAF neurla attention model for convexly optimal (artifically intelligent) success in computer vision research}
	{Divam Gupta, Varun Jain}
	{Keywords: none, haha, nono}
	{SIGBOVIK_2020_paper_17}
	{Retraction of a boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{Keywords: groove, in, retraction, the}
	{SIGBOVIK_2020_paper_18}
	{NaN-gate synthesis and hardware deceleration}
	{Keywords: hardware deceleration, hardware synthesis, electronic design automation, IEEE-754, NaN-gates, cat meme}
	{SIGBOVIK_2020_paper_19}
	{Optimizing the SIGBOVIK 2018 speedrun}
	{leo60228}
	{Keywords: speedrun, SIGBOVIK, pathfinding, DFS, Rust}
	{SIGBOVIK_2020_paper_20}
	{Sorting with human intelligence}
	{Cole Kurashige}
	{Keywords: sorting, algorithm, crowd sourcing, human intelligence}
	{SIGBOVIK_2020_paper_22}
	{Putting the ceremony in ``authentication ceremony''}
	{Camille Cobb, Sruti Bhagavatula}
	{Keyword: authentication, ceremony, fun, security, weddings}
	{SIGBOVIK_2020_paper_23}
	{Robot ethics:\@ Dangers of reinforcement learning}
	{Jake Olkin}
	{Keywords: deep reinforcement learning, ethics, simulation, spoof}
	{SIGBOVIK_2020_paper_24}
	{Type-directed decompilation of shell scripts}
	{Spencer Baugh, Dougal Pugson}
	{Keywords: partial evaluation, type systems, shell scripting}
	{SIGBOVIK_2020_paper_25}
	{MORSE OF COURSE:\@ Paper reveals time dimension wasted}
	{Dougal Pugson}
	{Keywords: Morse code, performance, Bash, protocols}
	{SIGBOVIK_2020_paper_26}
	{HonkFast, PreHonk, HonkBack, PreHonkBack, HERS, AdHonk and AHC:\@ The missing keys for autonomous driving}
	{Bernhard Egger, Max Siegel}
	{Keywords: awesome paper, best paper award, great reviewer 3, awesome reviewer 2, marvelous reviewer 1}
	{SIGBOVIK_2020_paper_27}
